---
output: github_document
---




<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# KapsarcR

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->


**This library is in early development, if you face any problem please open an issue**

R Client to access the data portal's API of King Abdullah Petroleum Studies and Research Center

The documentations of the API can be found [here](https://datasource.kapsarc.org/api/v2/console#!/)



## Installation


``` r
devtools::install_github("naif-alsader/KapsarcR")
```

## List Datasets


* list all datasets

```{r example}
library(KapsarcR)
library(tidyverse)

datasets<-list_datasets()

```


The dataset returned from `list_datasets()` is not tidy. You can use `clean_dataset()` to get a more tidy dataset


```{r}
datasets %>%
  clean_dataset() %>%
  head()
```

and the column names are

```{r, echo=FALSE}
datasets %>%
  clean_dataset() %>%
  colnames() 
```


* Filter the search

```{r, eval=FALSE}
# by Country
datasets<-list_datasets(country = "Saudi Arabia")

# by Theme
datasets<-list_datasets(theme  = "Water")

# by Keyword
datasets<-list_datasets(keyword  = "Water")


```


* Filter by two arguments

There are two ways filter two arguments:


1. if both arguments appear together (use operation = `and`) *the default value*


2. if either argument one or two appears (use operation = `or`)]

```{r, eval=FALSE}

datasets<-list_datasets(keyword  = "Water", theme = "Water", operation = "or")

```


* Filter using The Opendatasoft Query Language (ODSQL) 


```{r, eval=FALSE}
datasets<-list_datasets(q =  "default.theme = 'Water' or default.theme = 'Transportation'")


datasets<-list_datasets(q =  "default.modified > '2019'")


datasets<-list_datasets(q =  "default.records_count > 1000000")
```


The fileds that can be used in the query can be found in the meta column (its actually 4 datasets in one column) of the dataset `datasets$metas$default` or `datasets$metas$custom`

here is the complete list:

```{r, echo=FALSE}
datasets$metas$default  %>% colnames() %>% paste0("  default.", .) %>% pander::pander()
```

```{r, echo=FALSE}
datasets$metas$custom  %>% colnames() %>% paste0("  custom.", .) %>% pander::pander()
```

```{r,  echo=FALSE}

datasets$metas$dcat  %>% colnames() %>% paste0("  dcat.", .) %>% pander::pander()

```


## Retrive Datasets

* One dataset

```{r, eval=FALSE}
df <- get_dataset(datasets$dataset_id[1])
```


* All datasets that matches the search

```{r, eval=FALSE}
library(purrr)

df_list <- map(datasets$dataset_id, get_dataset)

```


## List attachments 

* One dataset's attachments

```{r, eval=FALSE}
attachments <- get_attachments(datasets$dataset_id[1])
```


* All datasets' attachments that matches the search


```{r, eval=FALSE}
attachments_list <- map(datasets$dataset_id, get_attachments)

```



## Download attachments

* One dataset attachments

```{r, eval=FALSE}
download_attachments(attachments)
```


* All datasets' attachments that matches the search

```{r, eval=FALSE}
map(attachments_list, download_attachments)
```


Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.
